% Note: this file can be compiled on its own, but is also included by
% diss.tex (using the docmute.sty package to ignore the preamble)
\documentclass[12pt,a4paper,twoside]{article}
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage[margin=25mm]{geometry}
\usepackage{graphicx}
\begin{document}

\vfil

\centerline{\Large Computer Science Project Progress Report}
\vspace{0.4in}
\centerline{\Large Pico without public keys}
\vspace{0.4in}
\centerline{\large S. Thang, St Edmund’s College}
\vspace{0.3in}
\centerline{\large 24 January 2016}

\vfil


\noindent
{\bf Project Supervisor:} Dr Graeme Jenkinson
\vspace{0.2in}

\noindent
{\bf Director of Studies:} Dr Robert Harle
\vspace{0.2in}
\noindent
 
\noindent
{\bf Project Overseers:} Dr~J.~Crowcroft \& Dr~T.~Sauerwald


% Main document

\section*{Progress Summary}


The project is currently behind schedule by approximately 1 task (2 weeks). The project is currently at the implementation of the Bonneau scheme. (Michaelmas weeks 6-8)

\section*{Difficulties and Solutions}

The original plan was to create a standalone module, then integration into the Pico codebase. The plan underestimated the time taken for integration, as Pico turned out to be a larger code base that was less modularized than expected. While implementing the standalone module proved to be very helpful in terms of understanding the entire symmetric key authentication process flow, most of the code had to be rewritten during the integration phase, taking up an additional 2-3 weeks. As a result, the project has slid behind.

The plan also did not realize the need to update the Pico Android UI/browser extensions to accommodate the new authentication method, which are simple but very time-consuming tasks to do right due to the relatively complex architecture in place. My supervisor and I have agreed that it is not central to the goals of the project, and have implemented simple workarounds that would reduce the amount of UI/browser extension work. These workarounds include: 

\begin{enumerate}

\item Hardcoding the username/password/server/client private key – these can be communicated out of band, and is a problem already solved by Pico.

\item Skipping the use of a rendezvous channel between Pico and the browser (which is more secure), passing the nonce directly via QR code instead.

\end{enumerate}

\section*{Workplan Amendments}

My supervisor and I have agreed that the extension "Credentials revocation" (Lent weeks 6-8) is to be removed from the workplan, as it's not feasible within the current timescale.

\end{document}
